### 2017-03-31 autocontrol_review/response_letter.tex

% Adjust margins for aesthetics
\addtolength{\voffset}{-0.5in}
\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{Chandrashekar Lakshminarayanan} % Your name for the signature at the bottom

@@

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{} % Name/title of the addressee

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{\textbf{Dear Editor,}}
We would like to re-submit the revised version of our paper. We now list the differences between the previous and current submission.
\begin{itemize}
\item The title of the paper has been changed to ``A Linearly Relaxed Approximate Linear Program for Markov Decisions Processes''.
\item The length of current draft has been increased to 8 pages.
\item We have incorporated major revisions in the paper and restructured the presentation.
\item The length of the introduction has been increased to make the motivation clear. Proper placement with respect to existing literature has been done.
\item The main result has been stated upfront alongside a discussion.
\item Streamlined formulation of the main result, with additional corollary that illustrates the utility. Added examples.
\item The proof has been simplified and restructured.
\item Numerical illustration: New example has been added to illustrate the choices available when choosing constraints.
\end{itemize}
We have taken care of all the reviewer comments, except for the following comment by Reviewer~$2$.\\
\emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.\\
\emph{Our Response:} The fact follows from the Markov property. Since we are limited by space, we have added a reference to literature.

### 2017-03-31 supplementary/intro.tex
single column supplementary updated

A popular approach along these lines, which goes back to \citet{SchSei85}, 
relies on considering linear approximations to the \emph{optimal value function}:
The idea is that, similarly to linear regression, a fixed sequence of basis functions are combined
linearly. The user's task is to use a priori knowledge of the MDP 
to choose the basis functions so that 
a good approximation to the optimal value function will exist in the linear space spanned by the basis functions.
The idea then is to design some algorithm to find the coefficients of the basis functions that gives a a good approximation, 
while keeping computation cost in check.
Finding a good approximation is sufficient, since at the expense of an extra $O(1/\epsilon^2)$ randomized computation, 
a uniform $O(\epsilon)$-approximation 
to the optimal value function can be used to calculate an action of an $O(\epsilon)$-optimal policy at any given state
(e.g., follow the ideas in \cite{szepesvari2001,kearns2002sparse}; see also Theorem 3.7 of \citet{Kall17}).
Since the number of coefficients can be much smaller than the number of states, the algorithms that search
for the coefficients have the potential to run efficiently regardless of the number of states.

>>>>

A popular approach along these lines, which goes back to \citet{SchSei85}, 
relies on considering linear approximations to the \emph{optimal value function}:
The idea is that, similarly to linear regression, a fixed sequence of basis functions are combined
linearly. The user's task is to use a priori knowledge of the MDP 
to choose the basis functions so that 
a good approximation to the optimal value function will exist in the linear space spanned by the basis functions.
The idea then is to design some algorithm to find the coefficients of the basis functions that gives a good approximation,
while keeping computation cost in check.
Finding a good approximation is sufficient, since at the expense of an extra $O(1/\epsilon^2)$ randomized computation, 
a uniform $O(\epsilon)$-approximation 
to the optimal value function can be used to calculate an action of an $O(\epsilon)$-optimal policy at any given state
(e.g., follow the ideas in \cite{szepesvari2001,kearns2002sparse}; see also Theorem 3.7 of \citet{Kall17}).
Since the number of coefficients can be much smaller than the number of states, the algorithms that search
for the coefficients have the potential to run efficiently regardless of the number of states.
